Total Platform Cyber Protection

### 2016-06-23 paper.tex
finished proof reading 8.2.6, great job yeganeh

\subsubsection{Modeling and monitoring execution}
This subarea of application layer security concentrates on modeling, monitoring, and analyzing the execution of an application to verify that the system is executing as expected, and to detect any malicious behavior. This can be seen as a testing strategy towards application security.

@@

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, and Binary Analysis~\cite{Song2008}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C/C++ languages~\cite{Younan2012}.

@@

\subsubsection{Protection against malicious code}
One of the challenging areas of application security is allowing arbitrary code execution without having to compromise security. There are situations in which applications need to run user provided code, reuse codes that were written in a non-type-safe language or host another program. For instance, browsers running web applications or apps being uploaded to app stores. In order to run codes safely and making sure that they are not executing malicious code, there are number of protection mechanisms that can be used, one of which is Sandboxing. it is also known as Software Fault Isolation (SFI)~\cite{Wahbe1993}. The idea is to run the code in an isolated environment within the applications address space called fault domain and then prevent the code from accessing outside of that fault domain.

Early research is focused on rewriting unsafe instructions and providing interface for system calls to restrict program's access~\cite{Wahbe1993,Mccamant2006}. Native Client (NaCl)~\cite{Yee2009a} is a sandbox provided by Google that offers x86 untrusted Native code execution in Chrome browser using x86 memory segmentation. Therefore, web developers can leverage the performance of executing native code in a safe environment. Xax~\cite{Douceur2008} is another similar technology that is in form of a browser plug-in that provides an abstraction layer for OS system calls. Other research extends this technology by covering ARM and x86-64~\cite{Zhao2011, Sehr2010,Ansel}. Others attempt to reduce the overhead of performing binary rewriting and memory isolation~\cite{Ford2008,Jana2011}. Sandboxing is also used for executing untrusted native code in Android applications~\cite{Sun2014,Afonso2016}.

The other approach towards protecting against malicious code is to analyze the code and detect malicious behavior~\cite{Zhou2012}. Despite all the efforts that have been made to keep malicious apps off the Android market, malicious apps can still find their way into the app store by bypassing the Google Bouncer~\cite{Lockheimer:2012} using different techniques. Bouncer uses sandboxing techniques to run apps in a confined environment, but researchers~\cite{oberheide2012dissecting} have shown that apps can fingerprint Bouncer and the environment in which they are being analyzed, using evasion and obfuscating techniques to complicate the reverse engineering process. If apps could detect that they are being analyzed, they can hold off on running their malicious code while being analyzed. A lot of research has been done to fingerprint the Android analyzers to show that evading detection is possible~\cite{Maier2014,Jing2014,Vidas2014}. Other approaches are using analysis to detect logic bombs, that is, when an application changes its behavior under certain conditions~\cite{Fratantonio2016}.

>>>>

\subsubsection{Modeling and monitoring execution}
This subarea of application layer security concentrates on modeling, monitoring, and analyzing the execution of an application to verify that the system is executing as expected, and to detect any malicious behavior. This can be seen as a testing strategy toward application security.

@@

There has been significant research in the area of analysis of an application. Dynamic analysis~\cite{ball1999concept} analyzes the code at run time, and much research in this area has been into Taint-based tracking~\cite{Chang2008}, Anomaly Detection~\cite{Cova2007, li11:BLOCK, Li2012}, Context-sensitive sanitization for popular languages and templating languages~\cite{Saxena2011, Samuel2011}, and Binary Analysis~\cite{Song2008}. Other work has looked at automated attack generation using model checking~\cite{martin08:goal_directed_mc}, and classifying the available countermeasures for the C and C++ languages~\cite{Younan2012}.

@@

\subsubsection{Protection against malicious code}
One of the more challenging areas of application security is allowing arbitrary code execution without compromising security. There are situations in which applications need to run user provided code, reuse code that was written in a non-type-safe language, or host another program. For instance, browsers running web applications, or apps being uploaded to app stores. To run code safely and make sure that they are not executing malicious code, there are a number of protection mechanisms that can be used, one of which is Sandboxing, also known as Software Fault Isolation (SFI)~\cite{Wahbe1993}. The idea is to run the code in an isolated environment within the application's address space (called fault domain) and then prevent the code from accessing addresses outside that fault domain.

Early research was focused on rewriting unsafe instructions and providing interfaces for system calls to restrict program's access~\cite{Wahbe1993, Mccamant2006}. Native Client (NaCl)~\cite{Yee2009a} is a sandbox provided by Google that offers x86 untrusted Native code execution in Chrome browser using x86 memory segmentation. Therefore, web developers can leverage the performance of executing native code in a safe environment. Xax~\cite{Douceur2008} is another similar technology that is in form of a browser plug-in that provides an abstraction layer for OS system calls. Other research extends this technology by covering ARM and x86-64~\cite{Zhao2011, Sehr2010, Ansel}. Others attempt to reduce the overhead of performing binary rewriting and memory isolation~\cite{Ford2008, Jana2011}. Sandboxing is also used for executing untrusted native code in Android applications~\cite{Sun2014, Afonso2016}.

The other approach toward protecting against malicious code is to analyze the code and detect malicious behavior~\cite{Zhou2012}. Despite all the efforts that have been made to keep malicious apps off the Android market, malicious apps can still find their way into the app store by bypassing the Google Bouncer~\cite{Lockheimer:2012} using different techniques. Bouncer uses sandboxing techniques to run apps in a confined environment, but researchers~\cite{oberheide2012dissecting} have shown that apps can fingerprint Bouncer and the environment in which they are being analyzed, using evasion and obfuscating techniques to complicate the reverse engineering process. If apps could detect that they are being analyzed, they can hold off on running their malicious code while being analyzed. A lot of research has been done to fingerprint the Android analyzers to show that evading detection is possible~\cite{Maier2014, Jing2014, Vidas2014}. Other approaches use analysis to detect logic bombs, i.e., when an application changes its behavior under certain conditions~\cite{Fratantonio2016}.
